\vspace{1.0cm} \LARGE \bf fluB

### 2013-07-24 fluB.tex
Minor comment.

Influenza B viruses are increasingly being recognized as major contributors to morbidity attributed to seasonal influenza. 
Currently circulating influenza B isolates are known to belong to two antigenically distinct lineages (referred to as B/Victoria and B/Yamagata subtypes (comment - is subtype okay to use here?)) on the basis of haemagglutinin inhibition (HI) assays. 
Frequent reassortment between the segments of these two lineages has been noted in the past \cite{lindstrom1999}, but the effects of these reassortments have not been investigated in much detail.

>>>>

Influenza B viruses are increasingly being recognized as major contributors to morbidity attributed to seasonal influenza. 
Currently circulating influenza B isolates are known to belong to two antigenically distinct lineages (referred to as B/Victoria and B/Yamagata subtypes (comment - is subtype okay to use here? - \tbc{Unfortunately, `subtype' is not kosher to refer to Vic and Yam.  It's annoying.  The most common term in the literature is `lineage'.  I suspect you could also get away with `virus', as in the `B/Vic virus'.})) on the basis of haemagglutinin inhibition (HI) assays. 
Frequent reassortment between the segments of these two lineages has been noted in the past \cite{lindstrom1999}, but the effects of these reassortments have not been investigated in much detail.
